\documentclass[11pt,a4paper,twocolumn]{article}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\title{\textbf{Two Dimensional Bin Packing Problem with Due Date}}
\author{\textbf{Milad Dehghan}\\
Isfahan University of Technology, Department of Industrial \& Systems Engineering, Iran\\
email: \texttt{milad.april18@yahoo.com}\\
\and\textbf{Sergey Polyakovskiy}\\
Deakin University, Department of Computer Science, Faculty of Information Technology, Australia\\
email: \texttt{sergey.polyakovskiy@deakin.edu.au}
}
\date{}

\begin{document}
\maketitle

\section{Introduction}\label{section.intro}

In the year 2000, when I was just nine years old, I participated in a mathematics contest in which I could earn 1st place among the top students of elementary schools in Kurdistan province, Iran. After that, my family figured out that I am good at mathematics, so they encouraged me to focus more on this aspect during my education. My next challenge as a kid was being admitted to the best school in our province (National Organization for Development of Exceptional Talents). I got accepted to my dream school was a life-altering moment.It taught me that everything is achievable if you work hard. In 2008, I got my high school Diploma in Mathematics and Physics. I participated in the Nationwide Entrance Exam for public universities a few months later and ranked among the top 5\% out of 300,000 participants. According to $e^{i\pi}+1=0$, I am sure that this formula$ (w_{i},h_{i^{*}})$ is correct and meaningful. $$e=\lim_{n\to\infty} \left(1+\frac{1}{n}\right)^n=\lim_{n\to\infty}\frac{n}{\sqrt[n]{n!}} $$
\begin{equation}e=\sum_{n=0}^{\infty}\frac{1}{n!}\end{equation}
\begin{equation}e=1+\frac{2}{1+\frac{3}{5+\frac{4}{\ddots}}}\end{equation}

\section{Literature Review}\label{section.litre}
In the year 2000, when I was just nine years old, I participated in a mathematics contest in which I could earn 1st place among the top students of elementary schools in Kurdistan province, Iran. After that, my family figured out that I am good at mathematics, so they encouraged me to focus more on this aspect during my education. My next challenge as a kid was being admitted to the best school in our province (National Organization for Development of Exceptional Talents). I got accepted to my dream school was a life-altering moment. It taught me that everything is achievable if you work hard. In 2008, I got my high school Diploma in Mathematics and Physics. I participated in the Nationwide Entrance Exam for public universities a few months later and ranked among the top 5\% out of 300,000 participants.

\section{Conclusion}\label{section.concl}
I chose Industrial Engineering at the University of Kurdistan (UOK), the most reputable university in the Kurdistan province. Embodying a plethora of mathematical and physical concepts in Industrial Engineering motivated me to pursue my undergraduate studies in that field. The pleasure of understanding and learning made easy for me all the difficulties during my undergraduate years. In 2015, I participated in the Nationwide Master Exam for public universities and ranked among the out of 15,000 participants. I chose to pursue my graduate studies at Isfahan University of Technology (IUT), one of Iran's most prestigious higher education institutions. During my graduate studies at IUT, I enjoyed learning new courses that helped increase my knowledge about optimization problems, especially in supply chain and logistics. In this regard, my master's thesis was about designing a distribution network under the risk of disruption. My thesis was chosen as one of our department's best master's theses. The findings of my thesis were also published in the RAIRO-Operations Research journal (JCR, Q2, IF=3.037). Besides my research, I was a teaching assistant at IUT for two master's courses, including Operations Research and Fundamentals of Probability and Statistics for Engineering. I could improve my leadership, teamwork, and effective communication with students during this period.
I introduced my idea in \ref{section.intro}, and reviewed the literature in many articles in \ref{section.litre} and section.conclsection.introsection.litreconcluded my decision in \ref{section.concl}.


\end{document} 